The reference model approach in feature selection problems \vspace{.1in}

### 2019-06-04 paper/ref_approach.tex
first complete version

    \author{
    Federico Pavone, 
  Juho Piironen,
  Paul-Christian B\"{u}rkner
  and Aki Vehtari\footnote{Helsinki Institute for Information Technology HIIT,
  Department of Computer Science, Aalto University, Finland.}
  }

@@

\begin{document}
\maketitle
\begin{abstract}
We carry out a comparison of different methods of feature selection using or not what we call a reference model on top of the procedure, that is a model that describes well our data. We measure the performance and the stability of each method using both the standard approach, that simply relies on data, and the reference model one. We include different procedures in the comparison as a selection through high probability density posterior credibility intervals, a selection made by controlling the Q-value and the local false discovery rate. Finally, we include in the comparison also a real world data example. Results show an increased stability and a better performance of the selection in favour of the reference model approach.
\end{abstract}

@@

In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction. The necessity of carrying out the selection arises from different problematics. Sometimes the main objective of the analysis is doing prediction for future observations, thus the main focus in building the model is on the predictive performance. Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens, e.g. when we are operating on limited resources, and thus a sparser representation of the same model would be preferred. In addition to that, simpler models bring also advantages in terms of interpretability. The variable selection can also be seen as an inferential tool: some other times the interest is on knowing which are the variables that are meaningful, or relevant, in relation to the target variable of interest. This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology. A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease. The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.

Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism. Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones. The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{paper:tibshirani_lasso} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data. The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e. the reference model, as an approximation of the data generation mechanism. Such an idea is widely present in the literature with different names. For example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation. He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model. \cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance. \cite{paper:faraggi_nn} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups. \cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$. \cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.

@@

The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}. In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction. The best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients. The resulting problem is convex and thus many efficient optimisation algorithm are available. Following \cite{paper:goutis_projection}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels. In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values. Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model. \cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance with the reference model one.

@@

In this paper we bring motivations for the use of a reference model. A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process. As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression with a real world dataset. We argue that however the reference model has been used, it can be always seen acting as a filter on the observed data. Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure. We thus show the reference model benefits, regardless of what specific procedure is applied, using as a benchmark the normal means estimation problem. We apply different state-of-the-art methods comparing in each case the results basing the selection on the data or on the reference model. In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection. The results indicate how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it. We do recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures. We hope that this work can increase the attractiveness on this family of methods and, thus, it can be of interest to a large number of practitioners.
\\
We would like also the reader to note that besides the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.

@@

The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, i.e. to be able to construct a model, that is the reference model, whose description of a future observation distribution is comparable to the ``true'' data generation mechanism. In practice, any full-encompassing model which has a good predictive performance is a candidate reference model. General modelling guidelines apply also for the reference model, expect for the fact that no variable selection is carried out at this stage.

@@

--- OR ---

What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data. This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}. Also the general idea of the projection of the predictive can be seen under this perspective. Indeed, let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions. The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
\
\begin{equation} 
\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
\end{equation}
Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
\
\begin{equation} 
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
\end{equation}
where $p_{t}$ is the distribution of a new observation under the true data generation mechanism. Maximising the elpd of a model is equivalent to minimising the KL-divergence of its predictive distribution from the true data generation mechanism. Therefore the projection corresponds to maximising the elpd using as distribution of the true data generation mechanism the posterior predictive distribution of the reference model, i.e.:
\
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y} 
\end{equation}
Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e. the reference model posterior predictive distribution.

------------------

Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach that can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g. posterior predictive mean. Afterwards any method for feature selection can be used. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination. We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features. While with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.

@@

We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique. It is possible to identify a common and inevitable overhead though, that is the cost of fitting the reference model. In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost. In general, a full Bayesian model is advisable to have the best predictive performance, however including all the available features can be often quite computationally demanding. In such a case a first possible speed-up could be to use screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}. However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and thus many of them have to be included in the reference model anyway. Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use frequentist approach, if predictions are good enough.

@@

In this Section we show the benefits of the use of a reference model. We consider as reference problem the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations. Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations, the normal means problem can be written as follows:

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations. We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. \cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior. We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for the HDP posterior credible intervals using the regularised horseshoe prior. All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e. ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e. ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.

@@

Figure \ref{fig:k} shows the posterior medians for the shrinkage factors of each parameter, averaged after 100 data simulations. Relevant and non-relevant features are respectively highlighted in red and blue. The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise. Respectively on the y-axis and on the x-axis are depicted the shrinkage factors using the reference model approach or not. If the reference model did not make any difference, we would expect the points to lie on the diagonal. Non-relevant features happen to lie on average on the diagonal for all the simulated scenario, meaning not evident benefits coming from the reference model. Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals. Such benefit is proportional to the difficulty of the problem, that is it increase with lower correlation and number of observations. Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distribution of the shrinkage factors is due to the averaging over the 100 data simulations. In a single data realisation there would be more noise and the cluster would be closer and more overlapping.

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, book:efron}, the empirical Bayes median \citep{paper:EBmed} and the selection by posterior credible intervals. The control of the local false discovery rate is applied through the R-package \textit{locfdr} using splines with 7 degrees of freedom to fit the marginal density and selecting features with local false discovery rate under the value 0.2. Such a value is the common suggested one just for the fact that it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison. The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose highest probability density posterior credible interval does not include zero at the level 0.9.
\\
Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$. For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach. The best selection performance is on the top left corner, which means lowest false discovery rate and highest sensitivity. It is possible to note that regardless of the method used for the selection, the use of a reference model improves the quality diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting). In accordance with what we would expect, higher the number of observation and the correlation are, easier the selection is and thus the benefit of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate. Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree. We thus consider as non-relevant all the artificially added ones. When $n=70$ we observe an increment in terms of sensitivity, also the false discovery rate slightly increase, but in a lower amount. In all other bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate. We observe again that the benefits are more evident as the selection is more challenging (i.e. less number of observations).
\\
Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}. The benefit of the reference model are here marginal, small improvements can be observed, but overall not very noticeable.

@@

This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction. The reference model acts as an approximation of the data generation mechanism through its predictive distribution. Such approximation is generally less noisy than sample estimation available from the observed data, leading to the main benefits of the reference model approach. In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used. The overall benefits, consisting in stability and goodness of the selection, observed when using point predictions of the reference model instead of the observed data, independently of the specific method applied, motivate what we refer to as the reference model approach for the model reduction framework. Such approach translates into a family of different methods, some of which have been present in the literature for several years.
\\
In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}. The selection via projection resulted to be more stable and led to a sparser representation. After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.

\begin{itemize}
\item add future research
\item extend conclusions further
\end{itemize}

>>>>

    \author{
    Federico Pavone, 
  Juho Piironen,
  Paul-Christian B\"{u}rkner
  and Aki Vehtari \footnote{Helsinki Institute for Information Technology HIIT,
  Department of Computer Science, Aalto University, Finland.}
  }

@@

\begin{document}
\maketitle
\begin{abstract}
When a reference model is used to guide the variable selection problem, it acts as a noise-filter. We show how this translate into higher stability and goodness of the selection. We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods using or not the reference model. We include in our comparisons state-of-the-art complete selection procedures showing improved stability, false discovery rate and sensitivity of the selection, and also Bayesian methods controlling the amount of posterior shrinkage and bias. In addition to that we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
\end{abstract}

@@

In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction. The necessity of carrying out the selection arises from different problematics. Sometimes the main objective of the analysis is doing prediction for future observations, thus the main focus in building the model is on the predictive performance. Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens, e.g. when we are operating on limited resources, and thus a sparser representation of the model would be preferred. In addition to that, simpler models bring also advantages in terms of interpretability. Some other times, variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest. This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology. A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease. The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.

Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism. Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones. The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{paper:tibshirani_lasso} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data. The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e. the reference model, as an approximation of the data generation mechanism. Such an idea is widely present in the literature with different names; for example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation. He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model. \cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance. \cite{paper:faraggi_nn} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups. \cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$. 
%\cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.

@@

The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}. In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients. The resulting problem is convex and thus many efficient optimisation algorithm are available. Following \cite{paper:goutis_projection}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels. In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values. Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model. \cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.

@@

In this paper we bring motivations for the use of a reference model. A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process. As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression with a real world dataset. We argue that however the reference model is used, it can be always seen acting as a filter on the observed data. Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure. We thus show the reference model benefits, regardless of what specific procedure is applied, using as a benchmark the normal means estimation problem. We apply different state-of-the-art methods comparing in each case the results basing the selection on the data or on the reference model. In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection. The results indicate how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it. We do recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures. We hope that this work can increase the attractiveness on this family of methods and, therefore, it can be of interest to a large number of practitioners.
\\
We would like also the reader to note that besides the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.

@@

The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, i.e. to be able to construct a model, that is the reference model, whose description of a future observation distribution is comparable to the ``true'' data generation mechanism. In practice, any full-encompassing model which has a good predictive performance is a candidate reference model. General modelling guidelines apply also for the reference model, except no variable selection is carried out at this stage.

@@

%--- OR ---

%What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data. This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}. Also the general idea of the projection of the predictive can be seen under this perspective. Indeed, let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions. The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
%\
%\begin{equation} 
%\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
%\end{equation}
%Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
%\
%\begin{equation} 
%\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
%\end{equation}
%where $p_{t}$ is the distribution of a new observation under the true data generation mechanism. Maximising the elpd of a model is equivalent to minimising the KL-divergence of its predictive distribution from the true data generation mechanism. Therefore the projection corresponds to maximising the elpd using as distribution of the true data generation mechanism the posterior predictive distribution of the reference model, i.e.:
%\
%\begin{equation} \label{proj_as_filter}
%\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y} 
%\end{equation}
%Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e. the reference model posterior predictive distribution.

%------------------

Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach which can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g. posterior predictive mean. Afterwards any method for feature selection can be used. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination. We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features. Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.

@@

We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique. It is possible to identify a common and inevitable overhead though, that is the cost of fitting the reference model. In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost. In general, a full Bayesian model is advisable in order to have the best predictive performance, however including all the available features can be often quite computationally demanding. In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}. However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and thus many of them have to be included in the reference model anyway. Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use frequentist approach, if predictions are good enough.

@@

In this Section we show the benefits of the use of a reference model using as a benchmark the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations. Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$, the normal means problem consists in estimating the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations. We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.

\cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior. We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior. All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e. ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e. ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.

@@

Figure \ref{fig:k} shows the posterior medians for the shrinkage factors of each parameter, averaged after 100 data simulations. Relevant and non-relevant features are respectively highlighted in red and blue. The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise. Respectively on the y-axis and on the x-axis are depicted the shrinkage factors using the reference model approach or not. If the reference model did not make any difference, we would expect the points to lie on the diagonal. Non-relevant features happen to lie on average on the diagonal for all the simulated scenario, meaning not evident benefits coming from the reference model. Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals. Such benefit is proportional to the difficulty of the problem, that is it increases with lower correlation and number of observations. Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations. In a single data realisation there would be more noise and the cluster would be closer and more overlapping.

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, book:efron}, the empirical Bayes median \citep{paper:EBmed} and the selection by posterior credible intervals. The control of the local false discovery rate is applied through the R-package \textit{locfdr} using splines with 7 degrees of freedom to fit the marginal density and selecting features with local false discovery rate under the value 0.2. Such a value is the common suggested one just for the fact that it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison. The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.
\\
Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$. For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach. The best selection performance is on the top left corner, which means lowest false discovery rate and highest sensitivity. It is possible to note that regardless of the method used for the selection, the use of a reference model improves the quality diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting). In accordance with what we would expect, higher the number of observation and the correlation are, easier the selection is and thus the benefit of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate. Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree. We thus consider as non-relevant all the artificially added ones. When $n=70$ we observe an increment in terms of sensitivity, also the false discovery rate slightly increase, but in a lower amount. In all other bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate. We observe again that the benefits are more evident as the selection is more challenging (i.e. less number of observations).
\\
Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}. The benefit of the reference model are here marginal, small improvements can be observed, but overall not very notable.

@@

This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction. We want to highlight that the goal of this paper is not to provide a specific algorithm or procedure to carry out the selection, but rather to bring motivations and attentions to the general use of a reference model. 
\\
The reference model acts as an approximation of the data generation mechanism through its predictive distribution. Such approximation is generally less noisy than the sample estimation available from the observed data, leading to the main benefits of the reference model approach. In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used. The overall benefits we have showed independently of the specific method applied, consisting in stability and goodness of the selection, motivate what we refer to as the reference model approach for the model reduction framework. Such approach translates into a family of different methods, some of which have been present in the literature for several years.
\\
In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}. The selection via projection resulted to be more stable and led to a sparser representation. After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
\\
Whenever it is possible to come up with a reasonable reference model, our suggestion is to employ it when selecting models, because of its nature as baseline of the comparisons and its ability to improve the selection. Note that the main challenge in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
\\
All Bayesian models have been implemented using Stan \citep{paper:stan}, which uses HMC-NUTS sampler \citep{paper:NUTS} and allows full posterior Bayesian inference. The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.
